Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS J08354256-0819237 and 2MASS J18212815+1414010

### 2016-12-19 ms.tex
I added a best-fit model fit plot to the spectrum. Also, for the 2 term fit to the time series, I show a comparison between using 1 cosine term and 2 cosine terms.

\section{Example Posterior Distributions}

In Figure \ref{fig:postCosfit}, we show the posterior distributions of a sinusoidal model (Equation \ref{eq:cosfit}) fit to the data using \texttt{emcee} \citep{foreman-mackey2013emcee} for an example wavelength bin of 1.08~$\mu$m.
This wavelength bin is one of the high amplitude fits that is relatively unaffected by telluric contamination.
We impose priors on the amplitude $A_1$ so that it would be positive, $t_1$ would be less than the observation windows (to avoid multiple periodic solutions) and that the period $\tau$ would be between 0 and the observation window length.
The model parameters are close to Gaussian and the only visible correlation is between the time offset, $t_1$, and the rotation period $\tau$.

@@

>>>>

\pagebreak
\section{Example Posterior Distributions}

\subsection{Time Series}
In Figure \ref{fig:postCosfit}, we show the posterior distributions of a sinusoidal model (Equation \ref{eq:cosfit}) fit to the data using \texttt{emcee} \citep{foreman-mackey2013emcee} for an example wavelength bin of 1.08~$\mu$m.
This wavelength bin is one of the high amplitude fits that is relatively unaffected by telluric contamination.
We impose priors on the amplitude $A_1$ so that it would be positive, $t_1$ would be less than the observation windows (to avoid multiple periodic solutions) and that the period $\tau$ would be between 0 and the observation window length.
The model parameters are close to Gaussian and the only visible correlation is between the time offset, $t_1$, and the rotation period $\tau$.

@@

\clearpage
\pagebreak
\subsection{Amplitude Spectrum}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{best_fit_spec_2temp.pdf}
\caption{Maximum likelihood spectrum using an MCMC fit to the amplitude spectrum of 2MASS 1821.}\label{fig:ML2Tempfit}
\end{centering}
\end{figure}
